% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Work Experience at the top
\sectionTitle{Professional Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
			\experience
	{Today} {Senior Principal Applied Scientist}{Oracle India}{Bangalore}
	{Dec 2023}{My Role is to develop Large Multimodal Models for Language-Vision area keeping the Visual Grounding in perspective. Additionally we are also looking for rich modality representations for Video.
	}
	{LMM, Transformers, Diffusion Models }
	\emptySeparator
		\experience
	{Dec 2023} {Principle Machine Learning Engineer}{Singapore Research Center, Huawei}{Singapore}
	{Dec 2022}{
		My role is to conduct and coordinate Research Initiatives associated with Ad Creatives -- understanding the content of the Advertisements and the cognitive interactions between various Ad Elements and users. The area thus involves Computational Advertisement, Creatives Psychology, Computer Vision, Cognitive analysis and Bayesian Programming. Most of my work requires developing Deep Learning Vision Models, Text Attention Models involving Advertisements. I work extensively on Neural Architectures, Image Attention, Transformers, Saliency and Memorability.
	}
	{Torch, Bayesian Programming, Vision Transformers, CLIP, Denoising Diffusion }
	\emptySeparator
	\experience
	{Nov 2022} {Principle Machine Learning Engineer}{India Research Center, Huawei}{India}
	{May 2021}{
		\begin{itemize}
			\item Ad Creative -- Deep Learning-Driven Advertisement Creation. I work on Automatic Advertisement Creation; and Creative Ranking using various compositional aspects involving Advertisements. All factors, like -- Industry, Product, Market, Users, Arts; -- are involved. The system involved learning the causal impact of each component on the overall performance. My work further involves several CNN/Transfomer based tools for Visual Analysis, Cognitive Analysis, Bayesian Programming for Reasoning, a few NLP and Sequential tools for learning the text impact, and Graphical Neural Network for understanding the connection among components.
			\item Saliency Prediction -- Network Development to predict Saliency
			\item Blur Prediction -- Network Development to predict Blur
			\item Memorability -- Network Development to preduct Memorability
		\end{itemize}
	}
	{Torch, Advertisement,  VisionTransformers,  Memorability, Cognition, Denoising Diffusion}
	\emptySeparator
  \experience
    {Apr 2021}   {Machine Learning Developer}{Adobe}{India}
    {Apr 2020} {
                      \begin{itemize}
                        \item Sensei: ML Model development and deployment
                        \item Visual Similarity Model Development 
                        \item Panoptic Segmentation : Module development on Post Processing side.
                        \item Metric development for ML models.
                        \item Tensor Library development for a subset of PyTorch
                      \end{itemize}
                    }
                    {Torch, ONNX, CoreML, Keras, Tensorflow, CNN, LSTM, Clustering}
  \emptySeparator
  \experience 
  {Mar 2020}
  {Senior Software Developer | Machine Learning Engineer}
  {Adobe}{India}
  {Sep 2016}
  {
  	\begin{itemize}
  	
  	\item Lightroom Performance: Performance enhancement for Lightroom Classic Import, Grid, and Library
  	
  	\item Markov Decision Process-based Dynamic Algorithm for Import: Parallel Distributed Batch Allocation based on MDP.                     
  	
  	\item Performance Database for Lightroom: Light-weight embedded Performance Database that Profiles Lua code automatically.
  	
  	\item Common Table Expressions for folders, keywords. Facilitates very fast lightweight low latency queries.                
  	
  	\item Feature Prediction: Natural Language Model for Photographic Features. Predicts future features based on previous features.
  	
  	\item Analytics for Lightroom.
  	
  	\item ML Models for Churn analysis and Garbage Collection
  \end{itemize}
	}
  {XCode, Visual Studio, Lua, SqLite, R, Python, Keras, Torch, Hadoop, Hive, LSTM, Reinforcement Learning, Distributed Programming, Scheduling, Markov Decision Process}
  \emptySeparator
  
  \experience {Aug 2016} {Senior Software Developer | Machine Learning Engineer}{Flipkart}{India}{Aug 2015}    
  {
  	\begin{itemize}
  		
  		\item ML Model for Ad Click Prediction: CTR, CVR prediction and Ad Ranking
  		
  		\item Ad SDK for Mobile Platform
  	\end{itemize}
  }
{ Ads, Native Ads, Pandas, R, Ranking, Sampling, Android, Thompson Sampling, Distributed Programming}
\emptySeparator

  \experience {Jul 2015} {Senior Software Developer | Machine Learning Engineer}{Qualcomm}{India}{Dec 2011}    
  {
	\begin{itemize}
		\item Optical Character Recognition for Indic (Devnagiri) Letters
		\item Online detection of interesting scenes in Camera
	\end{itemize}
  }
  { Computer Vision, C++, OpenCV, Android, Python, Assembly, Parallel Programming}
  
  \emptySeparator
 
  \experience {Nov 2011} {Software Developer}{Qualcomm}{India}{June 2008}    
	{
		\begin{itemize}
			\item Voice State Machine and Driver Development
		\end{itemize}
	}
	{ C++, Embedded Systems, Parallel Programming}

  \emptySeparator  
  \experience {May 2008} {Software Developer}{Texas Instruments}{India}{June 2006}    
	{
		\begin{itemize}
			\item Global Positioning Systems software development
		\end{itemize}
	}
	{ C++, Embedded Systems, Assembly Language}  	
	  
\emptySeparator
  
\end{experiences}
